Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-14 ms.tex
Fixing description of velocity profile

Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
($\Gamma=0.8$) solutions within our grid.  As expected, the gas
density increases towards the SMBH $\rho\propto r^{-n}$ with
$n\simeq1$.  Note that this is shallower than the $-3/2$ power law for
Bondi accretion. However, the power law behavior does not extend
through all radii, and the gas density profile has a break coincident
with the location of the break in the stellar light profile ($\rb=100$
pc). The temperature profile is relatively flat at large radii, but
increases as $\propto 1/r^{k}$ interior to the sphere of influence,
where $k$ is smaller than 1--the power expected for virialized gas.
The inwardly directed velocity increases towards the hole approaching
the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
interior to the sonic point, and then increases outwards towards large
radii.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...

>>>>

Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
($\Gamma=0.8$) solutions within our grid.  As expected, the gas
density increases towards the SMBH $\rho\propto r^{-n}$ with
$n\simeq1$.  Note that this is shallower than the $-3/2$ power law for
Bondi accretion. However, the power law behavior does not extend
through all radii, and the gas density profile has a break coincident
with the location of the break in the stellar light profile ($\rb=100$
pc). The temperature profile is relatively flat at large radii, but
increases as $\propto 1/r^{k}$ interior to the sphere of influence,
where $k$ is smaller than 1--the power expected for virialized gas.
The inwardly directed velocity increases towards the hole approaching
The inwardly directed velocity is steeper than what would be expected
for the free-fall velocity $v \propto v_{\rm ff}\propto r^{-1/2}$.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...
